MINOS Handover Plots

### 2023-06-01 minos/validation/handovers.Rmd

workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

```{r}
# Read raw datafiles in
raw.files <- list.files('/home/luke/Documents/WORK/MINOS/Minos/data/final_US/', pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

@@

save.path <- '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Handovers/'
```

>>>>

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- "/home/luke/Documents/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

```{r}
# Read raw datafiles in
raw.files <- list.files('/home/luke/Documents/MINOS/Minos/data/final_US/', pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

@@

save.path <- '/home/luke/Documents/MINOS/VALIDATION_PLOTS/Handovers/'
```
